\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS compatibility
\pdfgentounicode=1

% Custom commands (unchanged from your template)
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape João Pedro Carneiro de Morais} \\ \vspace{1pt}
    \small +1 (571) 568 1007  +351 962041130 $|$ \href{https://portfolio-plum-five-48.vercel.app/}{portfolio-plum-five-48.vercel.app} $|$ \href{mailto:jp.morais800@gmail.com}{jp.morais800@gmail.com}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeItemListStart
    \resumeItem{Final-year Computer Science student with expertise in full-stack development, specializing in React, JavaScript, and database management (MongoDB, MySQL, PostgreSQL).}
    \resumeItem{Currently interning at BRAINSTORM Labs, developing a video call feature using React, agora.io, Node.js, and Docker.}
    \resumeItem{Led a team of four in a hospital management software project, delivering functional modules on time using React, Node.js, and MongoDB.}
    \resumeItem{Fluent in English and Portuguese, with strong collaboration and leadership skills.}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Instituto Superior de Engenharia do Porto}{2021 -- Present}
      {B.S. Informatics Engineer $|$ \textbf{GPA}: 13.06/20.0}
      {Porto, Portugal}
      \resumeItemListStart
        \resumeItem{\textbf{Courses}: Web Development, Database Systems, Software Engineering, Data Structures and Algorithms}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    {\textbf{Front-end}: React, JavaScript, TypeScript, HTML, CSS, Tailwind CSS, Shadcn UI, Swift, SwiftUI}\\
    {\textbf{Back-end}: Node.js, Next.js}\\
    {\textbf{Databases}: MongoDB, MySQL, PostgreSQL, Supabase, Firebase}\\
    {\textbf{DevOps}: Docker}\\
    {\textbf{Tools \& Libraries}: Git, Clerk, Zod, Recharts}\\
    {\textbf{Programming Languages}: Java, C\#}}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Software Developmenter Intern}}{2025 -- Present}
      {BRAINSTORM Labs}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a video call feature using React, agora.io, PostgreSQL, Docker, Node.js, and Next.js, enhancing real-time communication for users.}
        \resumeItem{Integrated agora.io API for seamless video communication, managing user authentication and session handling.}
        \resumeItem{Collaborated with the development team to ensure smooth integration into the existing platform.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {\textbf{Nexus Finance}}{2025 -- Present}
      {Full Stack Project}{www.nexus-finance.live}
      \resumeItemListStart
        \resumeItem{Developed a personal finance dashboard for tracking stock and cryptocurrency investments, viewing market data, and following financial news.}
        \resumeItem{Implemented with Next.js, React, TypeScript, Supabase, Clerk authentication, Tailwind CSS, and Shadcn/ui.}
        \resumeItem{Utilized Recharts for data visualization, TanStack Query for data fetching, and Zod for schema validation.}

        \item[] {\vspace{0,1in}\small\textit{Note: I did not continue the project because building a real-time user dashboard proved too complex due to heavy regulations and constraints.}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{FamilySync}}{2025 -- Present}
      {iOS App Development}{}
      \resumeItemListStart
        \resumeItem{Building a comprehensive family management app to help families organize tasks, schedules, and expenses in a unified platform.}
        \resumeItem{Developing with Swift and Firebase.}
        \resumeItem{Implementing real-time updates and collaborative features for shared family information management.}

        \item[] {\vspace{0,1in}\small\textit{Note: The app is not in the App Store due to the subscription i would have to pay.}}
      \resumeItemListEnd

    \vspace{4pt}
    \resumeSubheading
      {\textbf{Queima25}}{2025 -- 2025}
      {iOS Game Development}{}
      \resumeItemListStart
        \resumeItem{Developed an interactive drinking game app in Swift featuring multiple game modes including timed challenges, never-have-I-ever scenarios, and custom rules.}
        \resumeItem{Implemented a robust game engine with dynamic phrase generation, player management, and category-based challenges.}
        \resumeItem{Created an engaging user experience with 200+ unique game phrases across 5 different categories (normal, warning, game, never, timed challenges).}

        \item[] {\vspace{0,1in}\small\textit{Note: The app is not in the App Store due to the subscription i would have to pay.}}
      \resumeItemListEnd
      
    \resumeSubheading
      {\textbf{Hospital Management Software}}{2024 -- 2025}
      {Full Stack Project}{}
      \resumeItemListStart
        \resumeItem{Led a team of four in designing and developing a hospital management system using React, Node.js, and MongoDB.}
        \resumeItem{Managed two backend systems to ensure data consistency and delivered functional modules (patient registration, appointment scheduling, medical records) on time.}
        \resumeItem{Utilized Git for version control and coordinated with team members to meet project deadlines.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd   
      

%-----------ADDITIONAL INFORMATION-----------
\section{Additional Information}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}: Fluent in English and Portuguese}
    \resumeItem{\textbf{Work Authorization}: EU citizen with U.S. permanent residency (Green Card)}
    \resumeItem{\textbf{GitHub Profile}: \href{https://github.com/JoaoMorais03}{github.com/JoaoMorais03} (Includes projects demonstrating full-stack development skills)}
  \resumeItemListEnd

\end{document} 